% An introduction to the problem the paper is aimed at solving
\section{Introduction to research problem}

This paper is aimed at solving the unpaired image-to-image translation problem and applying the technique in many tasks like collection style transfer, season transfer, photo enhancement, etc., where the paired training data does not exist.

Image-to-image translation is one of the main research areas in computer vision, which aims to produce an output image reflecting the style of target domain while keeping unrelated contents of the input source image unchanged. Common image-to-image translation tasks are multi-modal, single-modal and single-image image-to-image translation. Since Generative Adversarial model(GAN) has been proposed, it has been often used in image-to-image translation tasks, and has shown good performance.

When solving these image-to-image tasks, supervised setting with paired input-output training data is the most commonly used. However, in practice, obtaining paired data can be hard, for example it may be time-consuming and the desired output may not be well-defined sometimes, like the translation between photographs and pictures in Monet style. Therefore, in this paper, they have learned the relationship between domains, not pairs, i.e., the goal is to learn the mapping $G$: $X$ $\longrightarrow$ $Y$ given training samples $ {\{x_i\}}_{i=1}^N$ $\in$ $X$ and${\{y_j\}}_{j=1}^M$ $\in$ $Y$ in order to make distribution of images from $G(X)$ indistinguishable from the distribution of $Y$.

Although GAN is widely used in solving image-to-image problems, in the case of unpaired training data, it fails and needs modifications. The mapping $G$ and adversarial loss can just ensure that the distributions of $\hat{Y}$ and $Y$ are the same, but the individual $x$ and $y$ may not be paired up, and the optimization is difficult to make progress due to cases of mode collapse, for example, different inputs may get the same output. Therefore, a “cycle consistent” loss is added to the adversarial loss to prevent the learned mappings from contradicting each other. In the system, there is a translator $G: X $$\longrightarrow$$ Y $and its inverse $ F: Y $$\longrightarrow$ $X$, they are trained simultaneously with two discriminators $D_{X}$ and $D_{Y}$. The objective is the combination of Adversarial Loss and Cycle-Consistency Loss.

